### 2023-07-03 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
adding new excess pressure plots
fixing caption

\begin{figure}[H]
    \centering
    \subfigimg[width = 0.45\columnwidth]{(a)}{figures/Fig10a.pdf}
    \subfigimg[width = 0.45\columnwidth]{(b)}{figures/Fig10b.pdf}
    \caption{\small The excess pressure a single-component and a multicomponent vesicle moving through a stenosed channel. The reduced areas are (a) $\alpha = 0.4$, and (b) $\alpha = 0.6$.}
    \label{fig:excessPressure}
\end{figure}

>>>>

\begin{figure}[H]
  \centering
  \subfigimg[width = 0.49\columnwidth]{(a)}{figures/Excess_Pressure_RAp4}
  \subfigimg[width = 0.49\columnwidth]{(b)}{figures/Excess_Pressure_RAp6}
%    \subfigimg[width = 0.45\columnwidth]{(a)}{figures/Fig10a.pdf}
%    \subfigimg[width = 0.45\columnwidth]{(b)}{figures/Fig10b.pdf}
  \caption{\label{fig:excessPressure} \small The excess pressure a
  stiff single-component (red), floppy single-component (green), and a
  multicomponent (blue) vesicle moving through stenosis. The reduced
  areas are (a) $\alpha = 0.4$, and (b) $\alpha = 0.6$.}
\end{figure}
